Supplementary Figures and Tables

### 2021-01-24 Supplementary_fig_tab.Rmd
updated supplementary figure and table

# 4. Access to code

All codes are available at [github repo](https://github.com/selcenari/ceRNA_multifactorial_model).

>>>>

# 4. Notes and Access to code

+ *Table S7*: represents functional annotations of all highly perturbing genes from simulations of network retrieved from miRTarBase.

+ *Table S8*: represents functional annotations of tumor specific highly perturbing genes achieved from simulations of network retrieved from miRTarBase.

+ *Table S9*: represents functional annotations of tumor specific highly perturbing genes achieved from simulations of network retrieved from miRNA:target pairs that are validated by high-throughput experimental studies.

+ All codes are available at [github repo](https://github.com/selcenari/ceRNA_multifactorial_model).
